% any lines with a % are comment (the entire line)
%                    _      _____ _____ _    _ _______ _____ 
%                   | |    |_   _/ ____| |  | |__   __/ ____|
%                   | |      | || |  __| |__| |  | | | (___  
%                   | |      | || | |_ |  __  |  | |  \___ \ 
%                   | |____ _| || |__| | |  | |  | |  ____) |
%                   |______|_____\_____|_|  |_|  |_| |_____/ 
%                    lyrics (c) Lights Poxleitner 2008-2025
%
%                    lurker's little lights lyrics lottery
%
%           ~ Compiled by gcr and the rest of the Lights community ~
%          BIG THANKS to Elimand who tirelessly proofread ALL OF THEM
%
% These are all the lyrics that lurker might choose from. They should be short
% sentence fragments (less than 55 letters), and we only want the recognizable
% ones. Take pains to ensure corrections are as accurate as possible please! One
% lyric per line and order does not matter. No duplicates!
%
% Corrections? contact gcr or Elamind


% {{{ The last thing on your mind
Don't think too hard if you think it hurts that bad
Don't talk about it; don't let it get you down!
It's only one part of the story
Just let it go; don't let it bring you down now

Sing the last thing on your mind!
The last word on your breath!
I'll be the one to keep you!
I'll be the one to keep you one disaster less!

Straighten up your tie, take the microphone
Forget about it, don't let it get you down!
Now is not the time and you're not alone

I'll be okay! I'll be okay if you...
% }}}


% {{{ I Owe You One
What you've given me is more than I can say!
'Cause I don't know the words to thank you properly
You pulled me from the grave and stood me on a hill
When I was afraid, you made me still

For the love You bring
Owe You everything!
For the breath You give
You're my cause to live
For everything under the sun, I owe you one

Chaos all around! Explosions and fire!
You took me off the ground and lifted me higher!
% ...
Now I'll never be the same.
% }}}


% {{{ White
Are there oceans full of things you'll never say?
Are there skylines of the cities you don't see?
Is there music muted playing underneath?
Is mathematics keeping you from thinking free?

Do you see lights? Turn your shadows white!
Do you see lights?
Turn your shadows white!
Don't let rain clouds cry at all of your parades
Let the other side of darkness kiss your face

Into the sea! Into the sea.
All the things I want to say...
All the shadows in the way...
% }}}


% {{{ February Air
If you don't believe me, if you don't like my plans
% ... too long...
We walk the city
How I know your face like the back of my hand

My arms get cold in February air!
Please don't lose hold of me out there!

Say that you're with me
Say you know my face like the back of your hand
% }}}


% {{{ Drive my Soul
Seems somebody put out the moon
Now the road is a minefield
I can't follow the way she moves
I can't see past the shadows

You make the darkness disappear!
I feel found when you stand near
I know where I am when you are here!
My way becomes so clear...

When you're gone, will I lose control?
You're the only road I know!
You show me where to go!
Who will drive my soul?

Seems somebody burned up the signs
Where there's no borders, there are no lines!

You make the street lights reappear!
I feel bright when you stand near
I know what I am when you are here!
% }}}


% {{{ River
Out across cities, I see buildings burn into piles.
And watch the world in wonder as mountains turn into tiles
And trees losing their leaves, and our faces becoming tired
I wish I could discover something that doesn't expire!

Come and stumble me!

Take me river; carry me far!
Lead me, river, like a mother!
Take me over to some other unknown!
Put me in the undertow.

Such are the things that make a kingdom rumble and shatter
The same dynamic that another day would never matter
Things that don't make sense are always a little deceiving

I wanna go where you're going!
A follower following!
Changing but never changed!
Claiming but never claimed!
% }}}


% {{{ Ice
My mouth is frozen so I can't even speak!
What a disappointment, I had it perfectly!
What I was going to bring up suddenly
Stood like a stone as you stood quietly
You're making it hard for me! All I can do is freeze!

What I mean is all I need is just a little emotion
'Cause all I see is you not feeling
And you're giving me nothing nice!
I tried to do you right. Why'd you have to go and turn to ice?

I don't think you're knowing how hard this is for me
I'm not the type to say sorry constantly
So I swallowed my pride and I got on my knees
But still you just stood there as you stared at me
Your ego is getting old! How did you get so cold?

I'm looking at you looking at me, what can I do but say sorry?
It's a little late but you know I just want you to be happy!
What I got to say to make you let me get away with it this time?
I know you're upset and that you're happy just to sit and hate me!
But I'll make a bet that you'll be better to forget about me!
Even better yet, I'll let a little light melt the ice, ice baby!
% }}}


% {{{ Saviour
The night is deafening when the silence is listening
I'm down on my knees, and I know that something is missing.
% ... too long? ...
I'm a bit of a manic when it's not as I plan it
'Cause I start losing my head and then I get up in a panic
Are we denying a crisis or are we scared of admitting it?

I don't want to know

I just want to run to you
And break off the chains and throw them away!
I just want to be so much
And shake off the dust that turned me to rust!
Sooner than later, I'll need a saviour!
Save me!

It won't ever change if you want it to stay the same
% ... too long? ...

Stand me up and maybe I won't be so small!
Free my hands and feet and maybe I won't always fall...
%Save me!
% }}}


% {{{ The Listening
Please excuse me. I'm not thinking clear.
It must just be stress but I likely shouldn't be here!

I never really ever know what to say
I'm just trying to get us on the same page
I always get it better right afterwards
When all the wrong impressions are said and heard
How come I can never get the right words I need to convey?

% ...
I don't feel right

Can I let the trees do the talking?
Can I let the ground do the walking?
Can I let the sky fill what's missing, and...
Can I let my mouth do the listening?
% }}}


% {{{ Pretend
Once in a while, I act like a child
It gets like a prison in the body I'm living in
It would be nice to start over again before we were men

Let's play pretend
I'd give, I'd bend, let's play pretend
Remember the times we had soda for wine?
And we got by on gratitude.
The worst they could do to you was check your attitude
When fights were for fun, we had water in guns
How we lost hold of home, I guess I'll never know.

And when it's the end, our lives will make sense

It's not going to be long before we're all gone
Stop taking lives; come on, let's all grow up again!
% }}}


% {{{ Second Go
How many times will the clock go around?
How many times can my hands hit the ground?
How many coffins before there's a crown?
How far will I fall 'til the alarm sounds?

How can you love me when I am ugly?
Guess I can only hope

Give me a second go!
Don't let me go alone!
You saw me at the worst, You caught me falling first!

No matter the weather there's never a break!
Conquer a ladder then slip on a snake!
Cried 'til my river turned into a lake!
I'm wondering now before it's too late
How come you save me when I am angry?
Reasons I'll never know

One to five I'm half alive!
Six to nine I'm out of line.
Ten to twelve I'm not myself by the millionth time I cry.
% }}}


% {{{ Face Up
It's late and I am tired!
Wish I could spark a smile.
The place is flying high but right now I want to be low
Don't want to move an inch, let alone a million miles!
And I don't want to go but I know I've gotta go

I just want to feel alive!

The times you don't want to wake up
'Cause in your sleep it's never over when you give up
The sun is always going to rise up
%You need to get up, gotta keep your head up! %confusingly similar to below

Look at the people all around you!
The way you feel is something everybody goes through.
Dark out, but you still gotta light up!
You need to wake up, gotta keep your face up!

Seems like the more you grow, the more time you spend alone
Before you know it you end up perfectly on your own
The city's shining bright, but you don't see the light!
How come you concentrate on things that don't make you feel right?
%I just want to feel alright %similar to above

I'm looking for more than a little bit
I'm gonna have to find my way through it
Gonna leave a mark, I'm gonna set a spark
I'm coming up off the ground!
I won't be looking down.
% }}}


% {{{ Lions
Give me a disaster!
Give me emergency!
Stand me at the head of the crusade without a remedy!
Show me to the shipwreck!
Show me how your bones shake!
And when I'm at the edge of Sorrow's Blade
Show me how a heart breaks!

Be steady on your feet
No matter the trouble you meet

Lions make you brave
Giants give you faith
Death is a charade
You don't have to feel safe to feel unafraid

Find me at the bottom looking at the vultures
Standing in the heart of the disease
I'm looking for the thunder
I'm looking for the blackness
I'm learning how to get up off my knees
All it takes is practice

I'm not the hunter, I'm not the marked
Just looking for wisdom in the dark.
% }}}


% {{{ Quiet
I'm not yours and you're not mine
We can sit and pass the time
No fighting wars, no ringing chimes.
We're just feeling fine.

This is where we're supposed to be
Sitting by a broken tree
No tragedy, no poetry
Just staring at the sky

I could wait a thousand hours
Stay the same in sun and showers
Pick apart a hundred flowers
Just to be quiet
Tell me when you feel ready
I'm the one, there's not too many
Hold my hand to keep me steady
Just to be quiet with you

I like it here beside you dear
You're even more than you appear
And in the clouds my head is clear
Every time you say hello
So here's my heart and here's my mouth
I can't help if things come out
'Cause there are words I want to shout
But maybe I'll stay low...
% }}}


% {{{ My Boots
% see 
% http://www.iamlights.com/myboots?cmpid=110310/lyricvid/news
You might know if you're from around here
What goes on for half of the year
Have you seen the Queen of the Castle?
Paint this city from ear to fear

If the air was meant to be glitter
It might not take all yours away
When she swings, she's a heavy hitter!
When she comes, you'll ask her to stay!

Winter left a cover that I'm gonna end up under
I've got my boots
When I'm in a summer I forget how much I love her
It's a love hate-romance
'Cause I could watch her dance if I've got my boots!

A love hate-romance, I can't feel my hands
I got on my boots; got my boots on!
My boo-oo-oo-oo-oots!

Something in the way she comes gliding
Makes me need to fix up the hair!
She gets me to come out of hiding
And find something decent to wear!

Stop and stare...
% }}}


% {{{ Jess and Jonny
The car will get us there so you don't have to wait.
We'll drive, not walk, 'cause I know that you hate...
% awkward breaking
I love your face, your hair, regardless of your mood
We learn to talk it over 'til it's smooth
It really makes you brave, but we do it all the time
And I love you 'cause you're mine

So talk to me and make me feel fine!
I hope you can all the time

Forgive me if I'm ever on a knee
Kiss me if you're mad at mommy
Love me even if I'm a mess!
Take me as I am bad or best!
Love me even if I'm a mess! Take me as I am bad or best!
Jonny loves Jess!

There are a couple things -- we don't always agree
On what to watch or what we're going to eat
% is that awkward breaking?
But I'm willing to change for the sake of me and you
'Cause I know you're changing too

I try to think of how my life would probably be
Without you, I would feel so unhappy
'Cause you balance me out
You're the minus to my plus
You're the minus to my plus when it's just the two of us!
% }}}


% {{{ Romace Is
% this is the song that separates the men from the boys
% thanks to JuliGrande at http://board.iamlights.com/index.php?/topic/2081-romance-is-by-lights/page__p__48058__hl__%2Bromace+%2Blyrics__fromsearch__1%entry48058
You're three sides of my eight-sided circle
Two lovers juxtapose red doorways.
Broken window frames colour her eyes in with black lines
Let it all run down...

There's no explanation or forewarning
Underneath all the crimson linings
We approach the streets with the clear conscious we'll survive

It's one way to opt for a horizon
%               ^^^^^^^ hard to understand
It's one way to say we're abandoned
And we don't belong here at all
and romance just is

Slow it all down, the damage is done
Play the music loud, don't make a sound
Let's raise a toast to a sad story!
You made it hurt so bad
With a little poison, we can burn this whole place down
Burn this whole place down to the ground again
% }}}


% {{{ Pity scene
% thanks Elamind
I've come to realize that you've made up too many excuses
and I've come to see that I'm in this alone
You were only there when you wanted and I'm delirious
I'm at my wits end, and you're ignorant to refuse it
I don't understand why I'm in this alone.
Where's your heart in this matter?
Where's your hear--wha...?! oh wait I'm in drop D...
Black turns gray; ahead, ahead...
I played my part, if it matters
It's clear that I care too much today.
I care too much today
sorry I was in drop D for that one
and I hope you're hearing this
% }}}


% {{{ Casanova
% thanks Elamind
Cheap words falling out of your teeth
He heard, she heard, you heard me once
With a love gone sour
I've lost my appetite
There's no more flavor
In talking sweet, now fix it somehow
Don't Casanova me
I'm over you; it's over obviously
Don't put your sugar on me!
It's too late to sweeten this baby
Hey Casanova, it's over!
% }}}


% {{{ Year of the Cure
Are we all radicals painting our own lines?
Not at all practical, wasting our time?
Always going, never knowing
Give us a place to go where we can be found.
We're out of time to keep being lied to.
We all need to find a dream
We all dream about love
Cause these are the things we know for sure
To live without love is not what we're for
We'll make it the year we find the cure
So here we go heart and soul
Ready to burn down
I know I'm not ready to go home
No not when there's work to be done
% }}}


% {{{ Cactus in the Valley
% thanks susanxteasley
I never meant to wither, I wanted to be tall
Like a fool, I left the river and watched my branches fall

Old and thirsty, I longed for the flood to come back around
To the cactus in the valley; it's about to crumble down

Wipe the mark of sadness from my face!
Show me that Your love will never change!
If my yesterday is a disgrace, show me that You still recall my name.

So the storm finally found me and left me in the dark
In the cloud around me, I don’t know where You are
If this whole world goes up in arms, all I can do is stand
And I won’t fight for anyone until You move my hands

Wipe the mark of madness from my face!
% too similar to above?

Oh here, in the shadow; here I am.
And I need someone by my side!
It becomes so hard to stand and I keep trying to dry my eyes

Come and find me in the valley...

Tell me that You'll still recall my name.
% }}}


% {{{ Perfect
Maybe I don't say all the right things
Maybe I stumble on my words
Maybe I laugh at all the wrong times
Maybe I mumble and I curse
The last thing I want is to let you down
'Cause all I want is to make you proud!
But I'm perfect for you.
I can't explain just why I'm acting this way!
I can't control it, so I go with it.
I'm just a girl; I won't be changing the world.
And boy you know that I'm not perfect.
I know I don't make all the best moves
And I know sometimes I get weak
But I know I've got nothing to prove
Baby, that's what you love about me
The best I can do is to be myself
When you're in the room, my head is clear
And you'll make a world just disappear
Open up your eyes and see
% }}}


% {{{ The Horror
% see http://www.youtube.com/watch?v=BjK_ObeTzvo
% if you get one of these, gratz.
Save me from the horror!
I've been reading all of the wrong books
Filling my head with the wrong scenes
% }}}

% {{{ Fall Back Down
Don't worry about me, I'm gonna make it alright
Got my enemies cross-haired in my sight
Take a bad situation; gonna make it right
In the shadow of darkness, I stand in the light.
See, it's our style to keep it true
% abmiguous
%I've had a bad year, lag on through
%I've had a bad year, what I've gone through
Been knocked out beat down black and blue
She's not the one coming back for you

If you fall back down, you're gonna help me back up again
If I fall back down, you're gonna be my friend

It takes disaster to learn a lesson
%It takes disaster to learn a new lesson
Gonna make it through the darkest night
Some people betray you and then cause treason
Gonna make everything all right

The worst of times now? They don't phase me
Even if I act and look really crazy
On my way down, you betrayed me
Now my vision is no longer hazy
I'm very lucky to have my crew stood by me when she flew
% }}}

% {{{ You Got the Girl
% let's keep these out for now
% NOT PROOFREAD
%Hell, your grip is solid on me
%I'm delicate you know, I'm delicate I"m told
%Why can't you be careful with me?
%You never let me go, and I just can't say no
%'cause you are what I'm always missing
%what what can I do now
%I'm taken by you now
%
%you're sizing me up
%you're making me blush
%I'm not pretty enough
%
%I'm yours, hook and sinker,
%you know you win this round
%
%she's down, you're the winner this time,
%aren't you happy you got that girl
%I'm yours, song and singer, you know you won this round
%she's down, you're the winner tonight
%aren't you happy you got that girl
% }}}

% {{{ :D
I'd like to make myself believe
Because my dreams are bursting at the seams
if you can beat Elamind at this, you're a ninja
bet you puppies will never guess this lung disease: Pneumonoultramicroscopicsilicovolcanoconiosis
% }}}

% vim: foldmethod=marker:
